---
title: "Adding Quality Flags"
date: "`r Sys.Date()`"
author: "Thiloshon Nagarajah"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding Quality Flags}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
```

This document describes how quality flags of fields is added for a rgbif data. To begin:

* Ensure that you have an active internet connection. 

## Arguments

The function takes 4 optional arguments. 

```{r, eval = FALSE}
function(country = "AU",
             hasCoordinate = TRUE,
             limit = 5000,
             classKey = 121) 
```

* country: The 2-letter country code (as per ISO-3166-1) of the country in which the occurrence was recorded. See here http://en.wikipedia.org/wiki/ISO_3166-1_alpha-2

* hasCoordinate: (logical) Return only occurence records with lat/long data (TRUE) or all records (TRUE, default)

* limit: Number of records to return. Default: 5000

* classKey: (numeric) Class classification key. 121 is the classKey of "Animalia". (121, default)

## Dependencies 

The function uses 3 external libraries.

```{r, eval = FALSE}
library(rgbif)
library(rgeospatialquality)
library(plyr)
```

* rgbif: to connect with GBIF backbone and get occurance data

* rgeospatialquality: to add the flags. Function uses this library underneath to get the flags

* plyr: to combine splitted data in occasions of records of data being higher than 1000. rgeospatialquality takes only 1000 records in one request.
        
        
## Body    
        
`occ_data()` is used to get the data from GBIF. It returns 5 values and only the `data` is used in the function.
The column names of `data` is made lowercase from camelcase by `tolower()` so that the `rgeospatialquality` accepts the request. 

Since the `rgeospatialquality` accepts only 1000 records at one go, the data is divided into list by `split()` and `rep()`.

```{r, eval = FALSE}
stripData <- split(data, rep(1:5, each = round(NROW(data) / 5)))
```

Using `lapply()` the flag data is added. 

and finally `ldply()` is used to combine the list data into dataframe.
